External Prior Guided Internal Prior Learning for Real Noisy Image Denoising

### 2016-11-25 1047 - 副本.tex
add

% \cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{First Author\\
Institution1\\
Institution1 address\\
{\tt\small firstauthor@i1.org}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
\and
Second Author\\
Institution2\\
First line of institution2 address\\
{\tt\small secondauthor@i2.org}
}

>>>>

\cvprfinalcopy % *** Uncomment this line for the final submission

@@

\author{Jun Xu \qquad Lei Zhang \qquad David Zhang\\
Department of Computing, The Hong Kong Polytechnic University\\
{\tt \small{\{csjunxu,cslzhang,csdzhang\}@comp.polyu.edu.hk}}
% For a paper whose authors are all at the same institution,
% omit the following lines up until the closing ``}''.
% Additional authors and addresses can be added with ``\and'',
% just like the second author.
% To save space, use either the email address or home page, not both
%\and
%Second Author\\
%Institution2\\
%First line of institution2 address\\
%{\tt\small secondauthor@i2.org}
}
